Regular singular Volterra equations on complex domains

### 2023-08-10 reg-sing-volterra.tex
Split up bounds on perturbed kernel
Also, drop old versions of thm:basic_volterra and thm:proto-growth.

Our definition of a regular singularity implies that as $|\zeta|$ goes to zero, $|p|$ also goes to zero, while $|q|$ settles into a compact interval that doesn't include zero.
\begin{verify}
[\textit{Proof.} Fix any $a'$ in the neighborhood where the difference above is bounded. By confining $a$ to small enough neighborhoods of $\zeta = 0$, we can make $|\tau/\zeta(a)|$ arbitrarily large, forcing $|q(a')/p(a)|$ to become arbitrarily large to satisfy the definition. Since $a'$ is fixed, the only way for this ratio to get arbitrarily large is for $|p(a)|$ to get arbitrarily small.]
\end{verify}
For some of our results, we'll also need to control $|p|$ and $|q|$ in various ways as $|\zeta|$ goes to infinity.
\begin{conditions}
\condconst{slow}{\lambda_0}\label{cond:slow} We can find constants $\lambda_p$ and $\lambda_\text{ratio}$ with
\begin{align*}
\left|\frac{1}{p}\right| & \lesssim e^{\lambda_p |\zeta|} &
\left|\frac{q}{p}\right| & \le \lambda_\text{ratio}
\end{align*}
outside some neighborhood of $\zeta = 0$ in $\Omega$. Note that this only constrains the ratio of $p$ and $q$ when they're evaluated at the same point. The constants will only enter our reasoning through their sum, $\lambda_0 = \lambda_p + \lambda_\text{ratio}$.
\end{conditions}
This condition explains why $\domain$ might have the sort of shape illustrated in Section~\ref{setting:domain}. As $\domain$ stretches out toward infinity, it has to part around the zeros of $p$, keeping well away from every zero except the one at $\zeta = 0$.
\begin{conditions}
\condconst{diag$_0$}{\lambda_\Delta}\label{cond:diag-basic} We can find a constant $\lambda_\Delta$ with
\[ \big| \hardker(a, a') \big| \leq \,  \textcolor{magenta}{C_\Delta} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
over all $a$ in $\domain$ outside some neighborhood of $\zeta = 0$, and all $a' \in \domain$.
%%outside a neighborhood of $\zeta(a) = 0$ in $\domain^2$.
\end{conditions}
\subsubsection{The perturbed operator}\label{setting:perturbed}

@@

Since $\softpart$ is a holomorphic Volterra operator, $\softker$ is a holomorphic function on $\domain^2$. We'll allow $\softker(a, a')$ to have a simple pole at $\zeta(a) = 0$, like $\hardker(a, a')$ does, but we won't allow any sharper singularity. We'll also put an exponential bound on how fast $\softker$ grows away from the diagonal, mimicking Condition~\eqref{cond:diag-basic} on $\hardker$. Altogether, we'll require:
\begin{conditions}
\condconst{diag$_\star$}{\epsilon, \lambda_\Delta}\label{cond:eps-lambda} We have
\[ \big| \softker(a, a') \big| \leq \textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
over all $a, a' \in \domain$.
\end{conditions}
Notice that this condition prevents $\softker$ from being separable---unless it's zero, of course.

@@

\subsection{Main results}\label{sec:results}
We want to show that when $\volterra$ is a regular singular Volterra operator of the kind described in Section~\ref{setting:perturbed}, the equation $f = \volterra f$ has a unique solution of a certain form. For the prototypical operator $\hardpart$ described in Section~\ref{setting:basic}, this solution can be written explicitly.
\begin{thm}\label{thm:basic_volterra}
Suppose $\hardpart$ satisfies {\em Condition \eqref{cond:sing}}. Then the equation
\[ f = \hardpart f \]
has the {\em prototype solution}
\begin{equation}\label{eqn:test_solution}
\solproto(a)=\frac{p(b)}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right).
\end{equation}
Changing the base point $b \in \domain$ just multiplies $f_0$ by a non-zero constant.
\end{thm}
We'll prove this result in Section~\ref{sec:construction}.
\color{Tomato}
\begin{thm}%%\label{thm:basic_volterra}
Let $\hardpart$ be the operator described in Section~\ref{setting:basic} and assume it satisfies {\em Condition \eqref{cond:sing}}. Then the regular singular Volterra equation
\[ f = \hardpart f \]
have the {\em prototype solution}
\begin{equation}%%\label{eqn:test_solution}
f_0(a)=\frac{p(b)}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right).
\end{equation}
Changing the base point $b \in \domain$ just multiplies $f_0$ by a non-zero constant.

The magnitude $|f_0|$ is bounded by a constant multiple of $|\zeta|^{\tau-1}$ near $\zeta = 0$.

%%The solution $f_0$ scales like $\zeta^{\tau-1}$ as $\zeta$ goes to zero. To be precise, as $\zeta$ goes to zero, $|f_0/\zeta^{\tau-1}|$ settles into a compact interval that doesn't include zero.
\end{thm}
We'll prove this result in Section~\ref{sec:proto-construction-regularity}. Proposition~\ref{prop:construction} shows that $f_0$ is a solution, and Proposition~\ref{prop:asymptotic at zero} bounds it as desired near $\zeta = 0$.
\color{RoyalBlue}
\begin{rmk}
If $q$ has a limit at $\zeta = 0$, the solution $f_0$ from Theorem~\ref{thm:basic_volterra} can be written as a constant mutiple of $\zeta^{\tau-1}$ plus a function which is $O(\zeta^\tau)$ at $\zeta = 0$.

@@

Suppose $\hardpart$ also satisfies {\em Condition~\eqref{cond:slow}}. Then $f_0$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$ defined in Section~\ref{fn-spaces}.
\end{thm}
We'll prove this result in Section~\ref{sec:asymptotics}.
\color{Tomato}
\begin{thm}%%\label{thm:proto-growth}
Suppose $\hardpart$ satisfies both {\em Condition~\eqref{cond:sing}} and {\em Condition~\eqref{cond:slow}} from Section~\ref{setting:basic}. Then the solution $f_0$ from {\em Theorem~\ref{thm:basic_volterra}} is uniformly of exponential type $\lambda_0$.\footnote{Recall that a function is of exponential type $\Lambda$ if for every $\varepsilon>0$ there is a constant $A_\varepsilon$ (which depends on $\varepsilon$) such that $|f(x)|\leq A_\varepsilon e^{\Lambda+\varepsilon} $. We instead require that there exists a uniform constant $A$ such that for every $\varepsilon>0$ the bound holds.} In light of the behavior near $\zeta = 0$ described in, this tells us that $f_0$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$ defined in Section~\ref{fn-spaces}.
\end{thm}
We'll prove this result in Section~\ref{sec:proto-construction-regularity}, where it's restated as Proposition~\ref{prop:asymptotic at infinity}.
\color{black}
\begin{thm}\label{thm:general_volterra}
In the perturbed operator $\volterra = \hardpart +\softpart$ from Section~\ref{setting}, suppose the prototypical part $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}}, \eqref{cond:slow}, and \eqref{cond:diag-basic} from Section~\ref{setting:basic}, and the perturbation $\softpart$ satisfies Condition \eqref{cond:eps-lambda} from Section~\ref{setting:perturbed}. Then the Volterra equation
\[f = \volterra f\]
has a unique solution $f$ in the affine subspace
\[ f_0 + \singexpalg{\tau-1+\epsilon}(\Omega) \]
of the function space $\singexpalg{\tau-1}(\Omega)$ defined in Section~\ref{fn-spaces}. Here, $f_0$ is the prototype solution \eqref{eqn:test_solution} from Theorems \ref{thm:basic_volterra}--\ref{thm:proto-growth}, which belongs to the function space $\singexp{\tau-1}{\lambda_0}(\Omega)$.

@@

%%which is effectively finite-order over $\Omega$ in the sense of Definition~\ref{fin-order}, with order at least $1 + \epsilon$ for some $\epsilon \in (0, \infty)$.
\section{Solving holomorphic Volterra equations}
\subsection{Overview}
\begin{brainstorm}
\item Explain how we're going to prove Theorem~\ref{thm:general_volterra}.
\item Roughly follow the sections. Eventual goal: make section titles match proof steps.
\begin{itemize}
\item Link to subsections during description.
\end{itemize}
\item Rough sketch of proof story:
\begin{itemize}
    \item Construct prototype solution $f_0$. Show it's in $\singexp{\tau-1}{\lambda_0}$.
    \item Show that $\softpart$ maps $f_0$ into $\singexp{\tau-1+\varepsilon}{\Lambda}$ for $\Lambda\geq\lambda_\Delta$ (see Corollary \ref{cor:pertub_f0}).
    \item Show that $\volterra$ contracts $\singexp{\rho-1}{\Lambda}$ when $\rho > \tau$ and $\Lambda$ is big enough (done in Proposition \ref{prop:get-contraction}).
    \item Use the contraction mapping theorem to prove Lemma~\ref{lem:perturbed_volterra}, and then use that lemma to prove Theorem~\ref{thm:general_volterra}.
\end{itemize}
\end{brainstorm}
\subsection{Bounds on the perturbed kernel}\label{sec:bounds on k}
 When $\hardpart$ satisfies Condition \eqref{cond:sing} and $\softpart$ satisfies Condition \eqref{cond:eps-lambda}, we can estimate the kernel $k$ near $\zeta=0$. Let $\varepsilon>0$, we can choose $\delta$ such that for every $\zeta(a)<\delta$ and $\zeta(a') <\delta$

@@

@@

\begin{align*}
    |k(a,a')|&\leq |\hardker(a,a')| + |\softker(a,a')|\\
    &\leq \textcolor{magenta}{C_\Delta} e^{\lambda_\Delta |\zeta(a)-\zeta(a')|} +\textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\\
    &\leq \big(\textcolor{magenta}{C_\Delta} + \textcolor{magenta}{C_k}\, \delta |\zeta(a)-\zeta(a')|^\epsilon \big) \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
    %&\leq  \big(\textcolor{magenta}{C_\Delta} + \textcolor{magenta}{C_k}\, |\zeta(a)|^{\epsilon-1}\left\vert 1-\frac{\zeta(a')}{\zeta(a)}\right\vert^\epsilon \big) \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
\end{align*}
Since the growth of $|\zeta(a)-\zeta(a')|^\epsilon$ is polynomial, we can roughly estimate it by an exponential factor like

@@

\begin{verify}
    \begin{align*}
        \frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|} & \leq \frac{|\zeta(a)|^\epsilon + |\zeta(a')|^\epsilon}{|\zeta(a)|}\\
        &= |\zeta(a)|^{\epsilon-1}+ \delta |\zeta(a')|^\epsilon\\
        &\leq \delta^{\epsilon-1}+ \delta |\zeta(a')|^\epsilon 
    \end{align*}
\end{verify}

@@

is bounded by $C_1 \, |\zeta(a)|^\tau \, \exp\big(\tfrac{3}{2}\varepsilon\delta\big)$. Therefore, assuming $b'\in\Omega$ and $q(b') \neq 0$

\begin{align*}
|f_0| &  \leq C_1 |\zeta(a)|^\tau \, \exp\big(\tfrac{3}{2}\varepsilon\delta\big) \left\vert  \frac{p(b)}{p(a)}\right\vert \\
& =  C_2 |\zeta(a)|^\tau \, \left\vert\frac{p(q)}{q(b')} \right\vert \, \left\vert \frac{q(b')}{p(a)} \zeta(a)\right\vert \, |\zeta(a)|^{-1} \\
&  \leq C_3 |\zeta(a)|^{\tau-1}.
\end{align*}

@@

Let $\domain_\alpha$ be a simply connected open set $\domain_\alpha\subset\C$ that touches but doesn't contain $\zeta=\alpha$, and let $\Gamma_{\zeta, \alpha}^\theta$ be the ray that leaves $\zeta=\alpha$ at angle $\theta$. If $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, the Laplace transform $\laplace_{\zeta, a}^{\theta} $ maps functions in $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$ and $\Lambda\in\R$ to holomorphic functions in the half plane $\Re(z e^{-i\theta}) > \Lambda$~\cite[Section 5.6]{diverg-resurg-i}. It is defined by the formula

@@

    \begin{align*}
        \sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{| R_{r,j}|}{j!} \, \frac{|\zeta(a)-\zeta(a')|^j}{p(\zeta(a))}|\zeta(a')|^r  &\leq C_1 \sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{A^j}{j!} \, \frac{|\zeta(a)-\zeta(a')|^{j+1}}{|p(\zeta(a))|}|\zeta(a')|^r \\
        & =C_1 |\zeta(a)-\zeta(a')| \sum_{r=0}^{d-1} \frac{|\zeta(a')|^r}{|p(\zeta(a))|}\,  e^{A |\zeta(a)-\zeta(a')|}\\
        &=C_1 |\zeta(a)-\zeta(a')| \, \Big\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\Big\vert \sum_{r=0}^{d-1} \frac{|\zeta'|^r}{|q(\zeta(a'))|} \, e^{A |\zeta(a)-\zeta(a')|}\\
        &\leq C_2 |\zeta(a)-\zeta(a')| \, \Big\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\Big\vert \,  e^{A |\zeta(a)-\zeta(a')|}
    \end{align*}
now we notice that $\Big\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\Big\vert$ is bounded for $a,a'$ far from $\alpha$ by the argument we use in the proof of Condition \eqref{cond:diag-basic}. If $\zeta(a), \zeta(a')$ are close to $\alpha$ we can use Condition \eqref{cond:sing}

\[    \left\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\right\vert  \leq \left\vert \frac{q(\zeta(a'))}{p(\zeta(a))} -\frac{\tau_\alpha}{\zeta(a)-\alpha}\right\vert + \frac{\tau_\alpha}{|\zeta(a)-\alpha|}\leq C +  \frac{\tau_\alpha}{|\zeta(a)-\alpha|} \]

@@

\[\left\vert \frac{k_R(a,a')}{p(\zeta(a))}\right\vert\textcolor{magenta}{\lesssim} \frac{|\zeta(a)-\zeta(a')|}{|\zeta(a)-\alpha|}\, e^{2A |\zeta(a)-\zeta(a')} | \]

@@

Finally, we look closer to the prototype solution $f_{0,\alpha}$ from Theorem \ref{thm:basic_volterra}, Equation \eqref{eqn:test_solution}. Following the computation we did above we get that

\begin{align*}
    f_{0,\alpha}(a)&=\frac{p(b)}{p(a)} \exp\left(-\int_b^a\frac{q}{p} d\zeta\right)\\
    &=\frac{p(b)}{p(a)} \frac{(\zeta(a)-\alpha)^{\tau_\alpha}}{(\zeta(b)-\alpha)^{\tau_\alpha}} \exp\left(-\int_b^a\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha} d\zeta\right)\\
    &=(\zeta(a)-\alpha)^{\tau_\alpha-1} \frac{p(b)}{(\zeta(b)-\alpha)^{\tau_\alpha}} \frac{1}{p'(\alpha)+b_2'(\zeta(a)-\alpha)+b_3'(\zeta(a)-\alpha)^2}
\end{align*}

>>>>

Our definition of a regular singularity implies that as $|\zeta|$ goes to zero, $|p|$ also goes to zero, while $|q|$ settles into a compact interval that doesn't include zero.
\begin{verify}
[\textit{Proof.} Fix any $a'$ in the neighborhood where the difference above is bounded. By confining $a$ to small enough neighborhoods of $\zeta = 0$, we can make $|\tau/\zeta(a)|$ arbitrarily large, forcing $|q(a')/p(a)|$ to become arbitrarily large to satisfy the definition. Since $a'$ is fixed, the only way for this ratio to get arbitrarily large is for $|p(a)|$ to get arbitrarily small.]
\end{verify}
For some of our results, we'll also need to control $|p|$ and $|q|$ in various ways as $|\zeta|$ goes to infinity.
\begin{conditions}
\condconst{slow}{\lambda_0}\label{cond:slow} We can find constants $\lambda_p$ and $\lambda_\text{ratio}$ with
\begin{align*}
\left|\frac{1}{p}\right| & \lesssim e^{\lambda_p |\zeta|} &
\left|\frac{q}{p}\right| & \le \lambda_\text{ratio}
\end{align*}
outside some neighborhood of $\zeta = 0$ in $\Omega$. Note that this only constrains the ratio of $p$ and $q$ when they're evaluated at the same point. The constants will only enter our reasoning through their sum, $\lambda_0 = \lambda_p + \lambda_\text{ratio}$.
\end{conditions}
This condition explains why $\domain$ might have the sort of shape illustrated in Section~\ref{setting:domain}. As $\domain$ stretches out toward infinity, it has to part around the zeros of $p$, keeping well away from every zero except the one at $\zeta = 0$.
\begin{conditions}
\condconst{diag$_0$}{\lambda_\Delta}\label{cond:diag-basic} We can find a constant $\lambda_\Delta$ with
\[ \big| \hardker(a, a') \big| \lesssim e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
over all $a$ in $\domain$ outside some neighborhood of $\zeta = 0$, and all $a' \in \domain$.
%%outside a neighborhood of $\zeta(a) = 0$ in $\domain^2$.
\end{conditions}
\subsubsection{The perturbed operator}\label{setting:perturbed}

@@

Since $\softpart$ is a holomorphic Volterra operator, $\softker$ is a holomorphic function on $\domain^2$. We'll allow $\softker(a, a')$ to have a simple pole at $\zeta(a) = 0$, like $\hardker(a, a')$ does, but we won't allow any sharper singularity. We'll also put an exponential bound on how fast $\softker$ grows away from the diagonal, mimicking Condition~\eqref{cond:diag-basic} on $\hardker$. Altogether, we'll require:
\begin{conditions}
\condconst{diag$_\star$}{\epsilon, \lambda_\Delta}\label{cond:eps-lambda} We have
\[ \big| \softker(a, a') \big| \lesssim\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
over all $a, a' \in \domain$.
\end{conditions}
Notice that this condition prevents $\softker$ from being separable---unless it's zero, of course.

@@

\subsection{Main results}\label{sec:results}
We want to show that when $\volterra$ is a regular singular Volterra operator of the kind described in Section~\ref{setting:perturbed}, the equation $f = \volterra f$ has a unique solution of a certain form. For the prototypical operator $\hardpart$ described in Section~\ref{setting:basic}, this solution can be written explicitly.
\begin{thm}\label{thm:basic_volterra}
Suppose $\hardpart$ satisfies {\em Condition \eqref{cond:sing}}. Then the equation
\[ f = \hardpart f \]
has the {\em prototype solution}
\begin{equation}\label{eqn:test_solution}
\solproto(a)=\frac{p(b)}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right).
\end{equation}
Changing the base point $b \in \domain$ just multiplies $f_0$ by a non-zero constant.
\end{thm}
We'll prove this result in Section~\ref{sec:construction}.
\color{RoyalBlue}
\begin{rmk}
If $q$ has a limit at $\zeta = 0$, the solution $f_0$ from Theorem~\ref{thm:basic_volterra} can be written as a constant mutiple of $\zeta^{\tau-1}$ plus a function which is $O(\zeta^\tau)$ at $\zeta = 0$.

@@

Suppose $\hardpart$ also satisfies {\em Condition~\eqref{cond:slow}}. Then $f_0$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$ defined in Section~\ref{fn-spaces}.
\end{thm}
We'll prove this result in Section~\ref{sec:asymptotics}.
\begin{thm}\label{thm:general_volterra}
In the perturbed operator $\volterra = \hardpart +\softpart$ from Section~\ref{setting}, suppose the prototypical part $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}}, \eqref{cond:slow}, and \eqref{cond:diag-basic} from Section~\ref{setting:basic}, and the perturbation $\softpart$ satisfies Condition \eqref{cond:eps-lambda} from Section~\ref{setting:perturbed}. Then the Volterra equation
\[f = \volterra f\]
has a unique solution $f$ in the affine subspace
\[ f_0 + \singexpalg{\tau-1+\epsilon}(\Omega) \]
of the function space $\singexpalg{\tau-1}(\Omega)$ defined in Section~\ref{fn-spaces}. Here, $f_0$ is the prototype solution \eqref{eqn:test_solution} from Theorems \ref{thm:basic_volterra}--\ref{thm:proto-growth}, which belongs to the function space $\singexp{\tau-1}{\lambda_0}(\Omega)$.

@@

%%which is effectively finite-order over $\Omega$ in the sense of Definition~\ref{fin-order}, with order at least $1 + \epsilon$ for some $\epsilon \in (0, \infty)$.
\section{Solving holomorphic Volterra equations}
\subsection{Overview}
\begin{brainstorm}
\item Explain how we're going to prove Theorem~\ref{thm:general_volterra}.
\item Roughly follow the sections. Eventual goal: make section titles match proof steps.
\begin{itemize}
\item Link to subsections during description.
\end{itemize}
\item Rough sketch of proof story:
\begin{itemize}
    \item Construct prototype solution $f_0$. Show it's in $\singexp{\tau-1}{\lambda_0}$.
    \item Show that $\softpart$ maps $f_0$ into $\singexp{\tau-1+\varepsilon}{\Lambda}$ for $\Lambda\geq\lambda_\Delta$ (see Corollary \ref{cor:pertub_f0}).
    \item Show that $\volterra$ contracts $\singexp{\rho-1}{\Lambda}$ when $\rho > \tau$ and $\Lambda$ is big enough (done in Proposition \ref{prop:get-contraction}).
    \item Use the contraction mapping theorem to prove Lemma~\ref{lem:perturbed_volterra}, and then use that lemma to prove Theorem~\ref{thm:general_volterra}.
\end{itemize}
\end{brainstorm}
\subsection{Bounds on the perturbed kernel}\label{sec:bounds on k}
 When $\hardpart$ satisfies Condition \eqref{cond:sing} and $\softpart$ satisfies Condition \eqref{cond:eps-lambda}, we can estimate the kernel $k$ near $\zeta=0$. On the one hand, we can make the kernel $\hardker$ arbitrary close to $\frac{\tau}{|\zeta(a)|}$, by letting $a,a'$ close enough to $\zeta=0$. If we choose $\varepsilon>0$, we can choose $\delta$ such that for every $\zeta(a)<\delta$ and $\zeta(a') <\delta$

\begin{align*}
    |\hardker(a,a')| &\leq \left\vert\hardker(a,a')-\frac{\tau}{\zeta(a)} \right\vert +\frac{\tau}{|\zeta(a)|}\\
    &\leq \varepsilon +\frac{\tau}{|\zeta(a)|} 
\end{align*}

On the other hand, we can make the kernel $\softker$ arbitrary small by letting $a,a'$ close enough to $\zeta=0$. Assuming $|\zeta(a)|<\delta$ and $|\zeta(a')|<\delta$, by Condition \eqref{cond:eps-lambda}

\begin{align*}
    |\softker(a,a')|&\lesssim\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\\
    &\lesssim\frac{(2\delta)^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta (2\delta)}
\end{align*}

Hence, collecting these results together, if $a,a'$ are close enough to $\zeta=0$, there exists a constant $\sigma>\tau$ such that

\[
    |k(a,a')|\leq \frac{\sigma}{|\zeta(a)|}
\]

We'll use this fact is Sections \ref{sec:V is a contraction} and \ref{sec:existence and uniqueness}.

 \color{Tomato}

 Let $\varepsilon>0$, we can choose $\delta$ such that for every $\zeta(a)<\delta$ and $\zeta(a') <\delta$

@@

\color{black}

@@

\begin{align*}
    |k(a,a')|&\leq |\hardker(a,a')| + |\softker(a,a')|\\
    &\lesssim e^{\lambda_\Delta |\zeta(a)-\zeta(a')|} + \frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\\
    &\lesssim \big(1 + \delta |\zeta(a)-\zeta(a')|^\epsilon \big) \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
    %&\leq  \big(\textcolor{magenta}{C_\Delta} + \textcolor{magenta}{C_k}\, |\zeta(a)|^{\epsilon-1}\left\vert 1-\frac{\zeta(a')}{\zeta(a)}\right\vert^\epsilon \big) \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
\end{align*}
Since the growth of $|\zeta(a)-\zeta(a')|^\epsilon$ is polynomial, we can roughly estimate it by an exponential factor like

for some constant $M>0$.

\color{Tomato}
\begin{align*}
    |k(a,a')|&\leq |\hardker(a,a')| + |\softker(a,a')|\\
    &\leq \textcolor{magenta}{C_\Delta} e^{\lambda_\Delta |\zeta(a)-\zeta(a')|} +\textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\\
    &\leq \big(\textcolor{magenta}{C_\Delta} + \textcolor{magenta}{C_k}\, \delta |\zeta(a)-\zeta(a')|^\epsilon \big) \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
    %&\leq  \big(\textcolor{magenta}{C_\Delta} + \textcolor{magenta}{C_k}\, |\zeta(a)|^{\epsilon-1}\left\vert 1-\frac{\zeta(a')}{\zeta(a)}\right\vert^\epsilon \big) \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
\end{align*}
Since the growth of $|\zeta(a)-\zeta(a')|^\epsilon$ is polynomial, we can roughly estimate it by an exponential factor like

@@

\begin{verify}
    \begin{align*}
        \frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|} & \leq \frac{|\zeta(a)|^\epsilon + |\zeta(a')|^\epsilon}{|\zeta(a)|}\\
        &= |\zeta(a)|^{\epsilon-1}+ \delta |\zeta(a')|^\epsilon\\
        &\leq \delta^{\epsilon-1}+ \delta |\zeta(a')|^\epsilon 
    \end{align*}
\end{verify}
\color{black}

@@

is bounded by $ |\zeta(a)|^\tau$. Therefore, assuming $b'\in\Omega$ and $q(b') \neq 0$

\begin{align*}
|f_0| &  \lesssim |\zeta(a)|^\tau  \left\vert  \frac{p(b)}{p(a)}\right\vert \\
& \lesssim |\zeta(a)|^\tau \, \left\vert\frac{p(q)}{q(b')} \right\vert \, \left\vert \frac{q(b')}{p(a)} \zeta(a)\right\vert \, |\zeta(a)|^{-1} \\
&  \lesssim |\zeta(a)|^{\tau-1}.
\end{align*}

@@

Let $\domain_\alpha$ be a simply connected open set $\domain_\alpha\subset\C$ that touches but doesn't contain $\zeta=\alpha$, and let $\Gamma_{\zeta, \alpha}^\theta$ be the ray that leaves $\zeta=\alpha$ at angle $\theta$. If $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, the Laplace transform $\laplace_{\zeta, \alpha}^{\theta} $ maps functions in $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$ and $\Lambda\in\R$ to holomorphic functions in the half plane $\Re(z e^{-i\theta}) > \Lambda$~\cite[Section 5.6]{diverg-resurg-i}. It is defined by the formula

@@

    \begin{align*}
        \sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{| R_{r,j}|}{j!} \, \frac{|\zeta(a)-\zeta(a')|^j}{|p(\zeta(a))|}|\zeta(a')|^r  &\lesssim \sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{A^j}{j!} \, \frac{|\zeta(a)-\zeta(a')|^{j+1}}{|p(\zeta(a))|}|\zeta(a')|^r \\
        & \lesssim |\zeta(a)-\zeta(a')| \sum_{r=0}^{d-1} \frac{|\zeta(a')|^r}{|p(\zeta(a))|}\,  e^{A |\zeta(a)-\zeta(a')|}\\
        &\lesssim |\zeta(a)-\zeta(a')| \, \Big\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\Big\vert \sum_{r=0}^{d-1} \frac{|\zeta'|^r}{|q(\zeta(a'))|} \, e^{A |\zeta(a)-\zeta(a')|}\\
        &\lesssim |\zeta(a)-\zeta(a')| \, \Big\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\Big\vert \,  e^{A |\zeta(a)-\zeta(a')|}
    \end{align*}
now we notice that $\Big\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\Big\vert$ is bounded for $a,a'$ far from $\alpha$ by the argument we use in the proof of Condition \eqref{cond:diag-basic}. If $\zeta(a), \zeta(a')$ are close to $\alpha$ we can use Condition \eqref{cond:sing}

\[    \left\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\right\vert  \leq \left\vert \frac{q(\zeta(a'))}{p(\zeta(a))} -\frac{\tau_\alpha}{\zeta(a)-\alpha}\right\vert + \frac{\tau_\alpha}{|\zeta(a)-\alpha|}\lesssim 1 +  \frac{\tau_\alpha}{|\zeta(a)-\alpha|} \]

@@

\[\left\vert \frac{k_R(a,a')}{p(\zeta(a))}\right\vert \lesssim \frac{|\zeta(a)-\zeta(a')|}{|\zeta(a)-\alpha|}\, e^{2A |\zeta(a)-\zeta(a')|}  \]

@@

%Finally, we look closer to the prototype solution $f_{0,\alpha}$ from Theorem \ref{thm:basic_volterra}, Equation \eqref{eqn:test_solution}. %Following the computation we did above we get that

%\begin{align*}
 %   f_{0,\alpha}(a)&=\frac{p(b)}{p(a)} \exp\left(-\int_b^a\frac{q}{p} d\zeta\right)\\
  %  &=\frac{p(b)}{p(a)} \frac{(\zeta(a)-\alpha)^{\tau_\alpha}}{(\zeta(b)-\alpha)^{\tau_\alpha}} \exp\left(-\int_b^a\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha} d\zeta\right)\\
  %  &=(\zeta(a)-\alpha)^{\tau_\alpha-1} \frac{p(b)}{(\zeta(b)-\alpha)^{\tau_\alpha}} \frac{1}{p'(\alpha)+b_2'(\zeta(a)-\alpha)+b_3'(\zeta(a)-\alpha)^2}
%\end{align*}
